Climate-RWI relations

### 2018-10-26 analysis/rwi/climate_rwi_relate.Rmd
update

write.csv(rprec_all, here("/data/rwi_climate", "rprec_all.csv"), row.names = FALSE)
```

@@

```{r}
set.seed(3333)
rprec_SJ <- dcc(chrono = cro_sj, climate = prec_N, 
         method = "correlation",  boot = "std",
        .range(-9:10) + .sum(-9:8))

rprec_caL <- dcc(chrono = cro_caL, climate = prec_S, 
         method = "correlation",  boot = "std",
        .range(-9:10) + .sum(-9:8))

rprec_caH <- dcc(chrono = cro_caH, climate = prec_S, 
         method = "correlation",  boot = "std",
        .range(-9:10) + .sum(-9:8))

@@

rprec_all <- rprec_all %>% 
  mutate(month_name = case_when(
      month == "sep...AUG" ~ "Hydrol", 
      TRUE ~ as.character(.$month)))

>>>>

write.csv(rprec_all, here::here("/data/rwi_climate", "rprec_all.csv"), row.names = FALSE)
```

@@

```{r}
set.seed(3333)
rprec_SJ <- dcc(chrono = cro_sj, climate = prec_N, 
         method = "correlation",  boot = "std",
        .range(-9:10) + .sum(-9:8) + .sum(-12:2) + .sum(3:5) + .sum(6:8) + .sum(9:11))

rprec_caL <- dcc(chrono = cro_caL, climate = prec_S, 
         method = "correlation",  boot = "std",
        .range(-9:10) + .sum(-9:8) + .sum(-12:2) + .sum(3:5) + .sum(6:8) + .sum(9:11))

rprec_caH <- dcc(chrono = cro_caH, climate = prec_S, 
         method = "correlation",  boot = "std",
        .range(-9:10) + .sum(-9:8) + .sum(-12:2) + .sum(3:5) + .sum(6:8) + .sum(9:11))

@@
